Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-05-22 paper-amia-2018/manuscript.tex
update abstract, method, discussion and conclusion sections

\noindent{\bf Abstract}
\textit{Communication science approaches to developing effective behavior interventions, such as motivational interviewing (MI), are limited by traditionally manual qualitative coding of communication exchanges, which is a very resource-intensive and time-consuming process. This study focuses on the analysis of e-Coaching sessions, behavior interventions that are delivered via email and grounded in the principles of MI. A critical step towards automated annotation of e-Coaching communication exchanges is segmentation of emails into textual fragments that correspond to MI behaviors. In this work, we formulate this task as a classification problem and propose lexical, punctuation and topic features to address it. We experimented both with traditional machine learning methods, such as Support Vector Machine, Naive Bayes and K-Nearest Neighbor (KNN) classifiers and recurrent neural networks (RNNs). Experimental results indicate that KNN outperformed RNNs achieving 0.986 macro F1-score overall, and 0.779 and 0.993 macro F1-score for detecting ``new segment'' and ``same segment'' classes, respectively.}

@@

$$p(w|l) = {\sum_{z=1}^{K}{p(w|z,l)}}$$

@@

$$p(l|w) = \frac{p(w|l)p(l)}{p(w)}$$

where $p(l)$ is the prior probabilities of label $l$ in the training set and $p(w)$ is the prior probability of word $w$ in the language model estimated from the training set using maximum likelihood. We use the distribution $p(c|w)$ as the topical feature vector, which shows how indicative each word $w$ is for a particular behavior code $l$. Topical features allow to abstract away from individual words and detect segment boundaries by indirectly capturing transitions between behavior codes when only observing a pair of words that are specific to different behavior codes. Punctuation marks, which correspond to one of the symbols \{`.', `,', `!', `?', `:', `;', `-'\} between a pair of words, are also employed as a feature, since punctuation marks designate the boundary of a sentence, clause, and phrase and often also correspond to segment boundary.

@@

\textbf{Support Vector Machine}: state-of-the-art supervised classification method proven to be effective for text categorization\cite{joachims1998text} for its ability to cope with high dimensional input feature space. SVM finds the hyperplane that maximizes the separation between the closest ``new segment'' and ``same segment'' training examples. We used SVM with polynomial kernel in experiments.

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for identification of ``new segment'' class in e-Coaching emails. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{lexical features only}} & \multicolumn{3}{|c|}{\textbf{lexical + punctuation (+ topic features except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

 NB & 0.594 & 0.662 & 0.626 & 0.590 & 0.666 & 0.626 \\ \hline
 SVM & 0.742 & \textbf{0.679} & 0.709 & 0.774 & 0.696 & 0.733\\ \hline
 KNN & \textbf{0.808} & 0.663 & \textbf{0.728} & \textbf{0.820} & \textbf{0.742} & \textbf{0.779}\\ \hline
 LSTM & -- & -- & -- & 0.800 & 0.646 & 0.714  \\ \hline
 GRU & -- & -- & -- & 0.800 & 0.715 & 0.741 \\ \hline 
  \end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for identification of ``same segment'' class in e-Coaching emails. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_not_boundary}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{lexical features only}} & \multicolumn{3}{|c|}{\textbf{lexical + punctuation (+ topic features except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

 NB & 0.988 & 0.985 & 0.987 & 0.989 & 0.984 & 0.986 \\ \hline
 SVM & \textbf{0.989} & 0.992 & 0.991 & 0.990 & 0.993 & 0.991\\ \hline
 KNN & \textbf{0.989} & \textbf{0.995} & \textbf{0.992} & 0.991 & \textbf{0.994} & 0.993\\ \hline
 LSTM & -- & -- & -- & 0.993 & \textbf{0.994} & \textbf{0.994} \\ \hline
 GRU & -- & -- & -- & \textbf{0.994} & \textbf{0.994} & \textbf{0.994} \\ \hline 
  \end{tabular}
\end{table}

Table~\ref{tab:result_not_boundary} summarizes the performance of NB, SVM, KNN, and RNN models for detecting ``same segment'' class. We observed that performance is remarkably better for ``same segment'' class compared to new segment detection, which is expected, since 96.71\% instances belong to ``same segment'' class. KNN achieves 22.40\%, 50.07\%, and 36.26\% higher precision, recall, and F1-measure, respectively, for lexical features; and 20.85\%, 33.96\%, and 27.47\% higher precision, recall, and F1-measure, respectively, for combined features compared to new segment classification. In contrast to boundary detection, RNN demonstrates the highest performance among all models. LSTM obtains 0.993 precision with 0.994 recall and F1-measure while GRU has 0.994 for all performance metrics. The impact of punctuation and topic model-based features is consistent with ``new segment'' classification. Results indicate that F1-measure increases by 0\%, and 0.1\% for SVM and KNN models and decreases by 0.1\% for NB. \\

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods for segmentation of e-Coaching emails as a weighted average over ``same segment'' and ``new segment'' classification results. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|p{0.15\linewidth}|p{0.15\linewidth}|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{lexical features only}} & \multicolumn{3}{|c|}{\textbf{lexical + punctuation (+ topic features except RNN)}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-measure}\\ \hline

 NB & 0.975 & 0.974 & 0.975 & 0.976 & 0.974 & 0.975 \\ \hline
 SVM & 0.981 & 0.982 & 0.981 & 0.983 & 0.983 & 0.983\\ \hline
 KNN & \textbf{0.983} & \textbf{0.984} & \textbf{0.983} & \textbf{0.986} & \textbf{0.986} & \textbf{0.986}\\ \hline
 LSTM & -- & -- & -- & \textbf{0.986} & 0.983 & 0.984 \\ \hline
 GRU & -- & -- & -- & \textbf{0.986} & 0.985 & \textbf{0.986} \\ \hline 
  \end{tabular}
\end{table}

@@

\section*{Discussion}
This study is the first effort to evaluate the automatic segmentation of e-Coaching emails. Experimental results indicate that KNN is the best model among all machine learning methods considered for this study. KNN achieved 0.986 F1-measure in overall, 0.779 and 0.993 F1-measures for detecting ``boundary'' and ``not boundary'', respectively. The robust performance of KNN provides the evidence that machine learning models are capable to learn conceptual information from clinical exchange. It also indicates that topic features are more important than lexical features, even when deep learning methods are employed. Although the domain of this study was intentionally quite small, we believe that our study is not limited to the e-coaching domain, and it can be successfully applied to other domains, in which discourse segmentation is an preliminary step for annotation.

Punctuation mark and topic model-based features made a significant improvement in performance of all machine learning methods. In nearly all cases, ML methods perform better, when lexical features are used in combination with punctuation and topic model-based features. This results also indicate that segmentation performance might be improved by adding additional relevant features.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/roc-curves.png}
    \caption{\textbf{Receiver operating characteristic curves showing the performance of binary classifiers for the segmentation of e-coaching text when lexical features (left) and combination of lexical and other features (right) are used}.}
    \label{fig:roc-curves}
\end{figure}

In this paper, results are reported by each class to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall, and F1-measure were used to eliminate doubt about the model performance, since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. NB shows the highest AUC values, achieving 0.978 for both cases while provides lowest classification results. On the other hand, KNN and SVM exhibit 0.972 and 0.835 AUCs when only lexical features are used; and 0.959 and 0.844 AUCs when a combination of lexical, punctuation mark and topic model-based features are used. Finally, LSTM demonstrates lowest AUC values among all machine learning models, achieving 0.82 AUC, while GRU achieves 4.15\% higher AUC, than LSTM. The conclusion drawn from the ROC curves also confirmed the robustness and superiority of KNN model for the segmentation of clinical exchange.

We observed the second highest performance of RNN, in particular, LSTM and GRU for the text segmentation. We believe that RNN will perform better if a larger dataset is utilized. In this study, we employed 3,138 examples of boundary case which limit to achieve the best performance. We also observed that GRU performs better than LSTM, which was observed in previous studies\cite{chung2014empirical}.

Although punctuation mark plays an important role in segmentation boundary detection, and large numbers of errors were encountered by the false positive of boundary identification. For example, a text block ``A1 A2 A3. B1 B2 B3. C1 C2 C3 C4.'' can be incorrectly segmented at position A3, B3, and C4 where a punctuation mark was encountered. Similarly, additional information is the common reason for the classified original segment into multiple segments. For instance, the above text block can also be incorrectly segmented at position B3 and C4 because third sentence (C) only supports the MI code confirmed by first two sentences (A and B).

@@

\section*{Conclusion}
Segmentation of e-coaching emails is an integral part of developing e-Coaching interventions. Although several studies have focused on clinical interventions, they are limited by the qualitative coding of clinical interactions. In addition, previous studies in the medical domain mainly segmented clinical text into sections and sentences, none of them considered segmentation of text into groups of MI behaviors in the setting of discourse analysis with emails. In this paper, we compared the performance of machine learning models for the task of segmentation of e-coaching text. We found out that k-nearest neighbor provides the best performance for the segmentation of text in terms of all performance metrics. Manual segmentation of e-coaching data is very resource-intensive and time-consuming task, which can significantly decrease the time and effort required to develop an effective behavioral intervention. Our proposed methods can help to identify individual text segments, which can be annotated directly with a classification model. This approach will also help for developing fully automated e-coaching and accelerate the pace of identifying effective communication strategies.

>>>>

\noindent{\bf Abstract}
\textit{Communication science approaches to developing effective behavior interventions, such as motivational interviewing (MI), are limited by traditionally manual qualitative coding of communication exchanges, which is a very resource-intensive and time-consuming process. This study focuses on the analysis of e-Coaching sessions, behavior interventions that are delivered via email and grounded in the principles of MI. A critical step towards automated annotation of e-Coaching communication exchanges is segmentation of emails into textual fragments that correspond to MI behaviors. In this work, we formulate this task as a classification problem and propose lexical, punctuation and topic features to address it. We experimented both with traditional machine learning methods, such as Support Vector Machine (SVM), Naive Bayes and K-Nearest Neighbor (KNN) classifiers and recurrent neural networks (RNNs). Results indicate that SVM outperformed KNN and RNNs achieving 0.990 macro F1-score overall, and 0.848 and 0.995 macro F1-score for detecting ``new segment'' and ``same segment'' classes, respectively.}

@@

\begin{equation}
\label{eq:pwl}
p(w|l) = {\sum_{z=1}^{K}{p(w|z,l)}}
\end{equation}

@@

\begin{equation}
\label{eq:plw}
p(l|w) = \frac{p(w|l)p(l)}{p(w)}
\end{equation}

where $p(l)$ is the prior probabilities of label $l$ in the training set and $p(w)$ is the prior probability of word $w$ in the language model estimated from the training set using maximum likelihood. We use the distribution $p(l|w)$ as the topic feature vector, which shows how indicative each word $w$ is for a particular behavior code $l$. Topic features allow to abstract away from individual words and detect segment boundaries by indirectly capturing transitions between behavior codes when only observing a pair of words that are specific to different behavior codes. To find the optimal topic feature, we also derived the same topic feature $p(l|w)$ by using two recently proposed probabilistic generative latent variable models: Discriminative Labeled Latent Dirichlet Allocation (DL-LDA) and Latent Class Allocation (LCA)\cite{kotov2015interpretable}. Similar as L-LDA, DL-LDA-based topic feature is extracted by first deriving a label-specific language model $p(w|l)$ for each label $l$ from the word distributions $p(w|l,z)$ for topic $z$ specific to label $l$ by using the Eq.~\ref{eq:pwl} and \ref{eq:plw}. On the other hand, LCA directly provides label-specific multinomials $p(w|l)$, which can be used to derive topic feature by using Eq.~\ref{eq:plw}. Punctuation marks, which correspond to one of the symbols \{`.', `,', `!', `?', `:', `;', `-'\} between a pair of words, are also employed as a feature, since punctuation marks designate the boundary of a sentence, clause, and phrase and often also correspond to segment boundary.

@@

\textbf{Support Vector Machine}: state-of-the-art supervised classification method proven to be effective for text categorization\cite{joachims1998text} for its ability to cope with high dimensional input feature space. SVM finds the hyperplane that maximizes the separation between the closest ``new segment'' and ``same segment'' training examples. We used L1-regularized linear SVM with squared error minimization in experiments.

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, and KNN methods for identification of ``new segment'' and ``same segment'' classes as well as segmentation of e-Coaching emails as a weighted average over ``same segment'' and ``new segment'' in e-Coaching emails. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_base}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{new segment}} & \multicolumn{3}{|c|}{\textbf{same segment}}  & \multicolumn{3}{|c|}{\textbf{overall}} \\\cline{2-10}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline    
 \multicolumn{10}{|c|}{lexical features only} \\ \hline   
 NB & 0.594 & 0.662 & 0.626 & 0.988 & 0.985 & 0.987 & 0.975 & 0.974 & 0.975  \\ \hline
 SVM & 0.762 & \textbf{0.673} & 0.715 & \textbf{0.989} & 0.993 & 0.991  & 0.981 & 0.982 & 0.982 \\ \hline
 KNN & \textbf{0.808} & 0.663 & \textbf{0.728} & \textbf{0.989} & \textbf{0.995} & \textbf{0.992} & \textbf{0.983} & \textbf{0.984} & \textbf{0.983} \\ \hline
 \multicolumn{10}{|c|}{lexical and puctuation features} \\ \hline
 LSTM & \textbf{0.800} & 0.646 & 0.714  & 0.993 & \textbf{0.994} & \textbf{0.994} & \textbf{0.986} & 0.983 & 0.984 \\ \hline
 GRU & \textbf{0.800} & \textbf{0.715} & \textbf{0.741} & \textbf{0.994} & \textbf{0.994} & \textbf{0.994} & \textbf{0.986} & \textbf{0.985} & \textbf{0.986} \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, and KNN methods with different topic model's features for identification of ``new segment'' class in e-Coaching emails, when all three features are used together. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_boundary}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{L-LDA-based topic features}} & \multicolumn{3}{|c|}{\textbf{DL-LDA-based topic features}}  & \multicolumn{3}{|c|}{\textbf{LCA-based topic features}} \\\cline{2-10} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline

 NB & 0.573 & 0.680 & 0.622 & 0.573 & 0.677 & 0.621 & 0.593 & 0.662 & 0.626 \\ \hline
 SVM & 0.800 & 0.799 & 0.799 & \textbf{0.848} & \textbf{0.849} & \textbf{0.848} & 0.836 & 0.839 & 0.837  \\ \hline
 KNN & 0.808 & 0.741 & 0.773 & 0.814 & 0.732 & 0.771 & 0.814 & 0.740 & 0.775 \\ \hline
  \end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods with different topic model's features for identification of ``same segment'' class in e-Coaching emails, when all three features are used together. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_not_boundary}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{L-LDA-based topic features}} & \multicolumn{3}{|c|}{\textbf{DL-LDA-based topic features}}  & \multicolumn{3}{|c|}{\textbf{LCA-based topic features}} \\\cline{2-10} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline

 NB & 0.989 & 0.983 & 0.986 & 0.989 & 0.983 & 0.986 & 0.988 & 0.985 & 0.987 \\ \hline
 SVM & 0.993 & 0.993 & 0.993 & \textbf{0.995} & \textbf{0.995} & \textbf{0.995} & \textbf{0.995} & 0.994 & 0.994  \\ \hline
 KNN & 0.991 & 0.994 & 0.993 & 0.991 & 0.994 & 0.993 & 0.991 & 0.994 & 0.993 \\ \hline
  \end{tabular}
\end{table}

Table~\ref{tab:result_not_boundary} summarizes the performance of NB, SVM, KNN, and RNN models for detecting ``same segment'' class. We observed that performance is remarkably better for ``same segment'' class compared to new segment detection, which is expected, since 96.71\% instances belong to ``same segment'' class. KNN achieves 22.40\%, 50.07\%, and 36.26\% higher precision, recall, and F1-measure, respectively, for lexical features; and 20.85\%, 33.96\%, and 27.47\% higher precision, recall, and F1-measure, respectively, for combined features compared to new segment classification. In contrast to new segment detection, RNN demonstrates the highest performance among all models. LSTM obtains 0.993 precision with 0.994 recall and F1-measure while GRU has 0.994 for all performance metrics. The impact of punctuation and topic model-based features is consistent with ``new segment'' classification. Results indicate that F1-measure increases by 0\%, and 0.1\% for SVM and KNN models and decreases by 0.1\% for NB. \\

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM, KNN, and RNN methods with different topic model's features for segmentation of e-Coaching emails as a weighted average over ``same segment'' and ``new segment'' classification results, when all three features are used together. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{L-LDA-based topic features}} & \multicolumn{3}{|c|}{\textbf{DL-LDA-based topic features}}  & \multicolumn{3}{|c|}{\textbf{LCA-based topic features}} \\\cline{2-10} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline

 NB & 0.975 & 0.973 & 0.974 & 0.975 & 0.973 & 0.974 & 0.975 & 0.974 & 0.975 \\ \hline
 SVM & 0.987 & 0.987 & 0.987 & \textbf{0.990} & \textbf{0.990} & \textbf{0.990} & 0.989 & 0.989 & 0.989 \\ \hline
 KNN & 0.985 & 0.986 & 0.985 & 0.985 & 0.986 & 0.985 & 0.985 & 0.986 & 0.986 \\ \hline
  \end{tabular}
\end{table}

@@

\section*{Discussion}
This study is the first effort to evaluate the automatic segmentation of e-Coaching emails. Experimental results indicate that SVM is the best model among all machine learning methods considered for this study. SVM achieved 0.990 F1-measure in overall, 0.848 and 0.995 F1-measures for detecting ``new segment'' and ``same segment'', respectively. The robust performance of SVM provides the evidence that machine learning models are capable to learn conceptual information from clinical exchange. It also indicates that topic features are more important than lexical features, even when deep learning methods are employed. Although the domain of this study was intentionally quite small, we believe that our study is not limited to the e-Coaching domain, and it can be successfully applied to other domains, in which discourse segmentation is an preliminary step for annotation.

Punctuation mark and topic model-based features made a significant improvement in performance of all machine learning methods. Among all topic model-based feature, DL-LDA-based topic feature provides the highest performance in ``new segment'' and ``same segment'' classification as well as weighted average over ``new segment'' and ``same segment'' classification results. In nearly all cases, ML methods perform better, when lexical features are used in combination with punctuation and topic model-based features. This results also indicate that segmentation performance might be improved by adding additional relevant features.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/roc-curves.png}
    \caption{\textbf{Receiver operating characteristic curves showing the performance of binary classifiers for the segmentation of e-Coaching text when lexical features (left) and combination of lexical, DL-LDA-based topic, and punctuation features (right) are used}.}
    \label{fig:roc-curves}
\end{figure}

In this paper, results are reported by each class to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall, and F1-measure were used to eliminate doubt about the model performance, since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets\cite{hu2015kernelized}, which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}. NB shows the highest AUC values, achieving 0.978 for both cases while provides lowest classification results. On the other hand, KNN and SVM exhibit 0.972 and 0.833 AUCs when only lexical features are used; and 0.966 and 0.922 AUCs when a combination of lexical, punctuation mark and topic model-based features are used. Finally, LSTM demonstrates lowest AUC values among all machine learning models, achieving 0.82 AUC, while GRU achieves 4.15\% higher AUC, than LSTM. The conclusion drawn from the ROC curves also confirmed the robustness and superiority of KNN model for the segmentation of clinical exchange.

We observed moderate performance of RNN, in particular, LSTM and GRU for the text segmentation. We believe that RNN will perform better if a larger dataset is utilized. In this study, we employed 3,138 examples of boundary case which limit to achieve the best performance. We also observed that GRU performs better than LSTM, which was observed in previous studies\cite{chung2014empirical}.

Although punctuation mark plays an important role in segmentation boundary detection, and large numbers of errors were encountered by the false positive of boundary identification. For example, a text block ``A1 A2 A3. B1 B2 B3. C1 C2 C3 C4.'' can be incorrectly segmented at position A3, B3, and C4 where a punctuation mark was encountered. Similarly, additional information is the common reason for the classified original segment into multiple segments. For instance, the above text block can also be incorrectly segmented at position B3 and C4 if third sentence (C) only provides a supportive information of MI code associated with first two sentences (A and B).

@@

\section*{Conclusion}
Segmentation of e-Coaching emails is an integral part of developing e-Coaching interventions. Although several studies have focused on clinical interventions, they are limited by the qualitative coding of clinical interactions. In addition, previous studies in the medical domain mainly segmented clinical text into sections and sentences, none of them considered segmentation of text into groups of MI behaviors in the setting of discourse analysis with emails. In this paper, we compared the performance of machine learning models for the task of segmentation of e-Coaching text. We found out that SVM provides the best performance for the segmentation of text in terms of all performance metrics. Manual segmentation of e-Coaching data is very resource-intensive and time-consuming task, which can significantly decrease the time and effort required to develop an effective behavioral intervention. Our proposed methods can help to identify individual text segments, which can be annotated directly with a classification model. This approach will also help for developing fully automated e-Coaching and accelerate the pace of identifying effective communication strategies.
